\documentclass[main.tex]{subfiles}
\begin{document}
\begin{center}
\begin{longtable}{ |p{0.8cm}p{6.8cm}|p{0.8cm}p{6.8cm}|  }
 \hline
 \multicolumn{4}{|c|}{Instrumental ADL} \\
 \hline
 \textit{\textbf{Score}} & \textit{\textbf{Activities}} & \textit{\textbf{Score}} & \textit{\textbf{Activities}}\\
 \hline
 \vspace{0.15cm} & & &\\
 
  & \textbf{A. Ability to use telephone}  & & \textbf{E. Laundry}  \\
  
 1 & A.1 Operates telephone on own initiative; looks up and dials numbers, etc. & 1  & E.1 Does personal laundry completely \\
 
 1 & A.2 Dials a few well-known numbers & 0 &  E.2 Launders small items; rinses stockings, etc.\\
 
 1    & A.3 Answers telephone but does not dial & 0 & E.3 All laundry must be done by others.\\
 
 0 & A.4 Does not use telephone at all. & & \\
 
 \vspace{0.15cm} & & &\\

 & \textbf{B. Shopping} & & \textbf{F. Mode of Transportation} \\
 
 1 & B.1 Takes care of all shopping needs independently & 1 & F.1 Travels independently on public transportation or drives own cars. \\
 
 0 & B.2 Shops independently for small purchases & 1 & F.2 Arrange own travel via taxi, but does not otherwise use public transportation.\\
 
 0 & B.3 Needs to be accompanied on any shopping trip. & 1 & F.3 Travels on public transportation when accompanied by another.\\
 
 0 & B.4 Completely unable to shop. & 0 & F.4 Travel limited to taxi or automobile with  assistance of another.\\
 
 & & 0 & F.5 Does not travel at all.\\
 
 \vspace{0.15cm} & & &\\

 & \textbf{C. Food Preparation} & & \textbf{G. Responsibility for own medications}\\
 
 1 & C.1 Plans, prepares and serves adequate meals independently & 1 & G.1 Is responsible for taking medication in correct dosages at correct time.\\
 
 0 & C.2 Prepares adequate meals if supplied with ingredients & 0 & G.2 Takes responsibility if medication is prepared in advance in separate dosage.\\
 
 0 & C.3 Heats, serves and prepares meals or prepares meals but does not maintain adequate diet. & 0 & G.3 Is not capable of dispensing own medication.\\
 
 0 & C.4 Needs to have meals prepared and served. & & \\
 
 \vspace{0.15cm} & & &\\
  
 & \textbf{D. Housekeeping} & & \textbf{H. Ability to Handle Finances}\\ 
 
 1 & D.1 Maintains house alone or with occasional assistance (e.g. “heavy work domestic help”) & 1 & H.1 Manages financial matters independently (budgets, writes checks, pays rent, bills goes to bank), collects and keeps track of income.\\
 
 1 & D.2 Performs light daily tasks such as dish-washing, bed making & 1 & H.2 Manages day-to-day purchases, but needs
help with banking, major purchases, etc.\\

 1 & D.3 Performs light daily tasks but cannot maintain acceptable level of cleanliness. & 0 & H.3 Incapable if handling money.\\
 
 1 & D.4 Needs help with all home maintenance tasks. & & \\
 0 & D.5 Does not participate in any housekeeping tasks. & &\\
  
 \hline
 \caption{Instrumental Activities of Daily Living Scale \cite{lawton1970assessment}.}
 \label{tab:IADL}
\end{longtable}
\end{center}
\end{document}